---
title: "RSeq Report"
output: 
  html_document:
    code_folding: hide
    theme: flatly
    highlight: textmate
params:
  corr_data: "placeholder"
  anno_data: "placeholder"
  rlfs_data: "placeholder"
  rlcons_data: "placeholder"
  bam_stats: "placeholder"
  peak_ol: "placeholder"
  read_qc_data: "placeholder"
  configlist: "placeholder"
---

```{r setup, include=FALSE, echo=FALSE}
library(knitr)
library(kableExtra)
library(pheatmap)
library(ggpubr)
library(RColorBrewer)
library(ChIPpeakAnno)
library(regioneR)
library(grid)
library(plotly)
show_anno <- ifelse(tibble::is_tibble(anno_data), TRUE, FALSE)
show_corr <- ifelse(is.list(corr_data), TRUE, FALSE)
show_rlfs <- ifelse(is.list(rlfs_data), TRUE, FALSE)
sample_name <- configlist$sample_name
control <- ifelse(configlist$controls == "None", FALSE, TRUE)
mode_now <- configlist$mode
current_time <- date()
pe <- configlist$paired_end
genome <- configlist$genome
strand <- configlist$strand_specific
strandedness <- ifelse(strand, "stranded", "unstranded")
moiety <- configlist$moeity
ip_type <- configlist$ip_type
```

<br>

Sample name: <strong>`r sample_name`</strong>

Sample type: <strong>`r paste0(mode, "-Seq")`</strong>

Genome: <strong>`r genome`</strong>

Time finished: <strong>`r current_time`</strong>

***

## Summary

```{r}
# # TODO: Put real link later
# rmap_samples <- read_csv("https://raw.githubusercontent.com/millerh1/RMapDB/development/data/RMapDB_samples_10_22_2020.csv?token=AKV4343ZBQUD72AZ2RCFTXS7VVYKW")
# # Median correlation of user sample to samples of the same mode, exluding control samples (e.g., RNaseH1).
# corr_score <- data.frame("clean_name" = rownames(corr_data$annoNow), "R" = corr_data$corMat[sample_name,]) %>%
#   inner_join(y = rmap_samples, by = "clean_name") %>%
#   dplyr::filter(mode == mode_now & ! Condition %in% c("IgG", "RNaseH1", "RNASEH1", "RNH-high", "WKKD")) %>%
#   pull(R) %>%
#   median() * 100
# # RLFS score. LogP * zscore * kurtosis / absolute skew + 1
# pval <- rlfs_data[[1]]$`regioneR::numOverlaps`$pval
# pval <- ifelse(pval > .05, 1, pval)
# pval <- -log10(pval)
# minpvalpossible <- -log10(1/(1+rlfs_data[[1]]$`regioneR::numOverlaps`$ntimes))
# zscore_summit <- rlfs_data[[1]]$`regioneR::numOverlaps`$zscore
# zscores <- rlfs_data[[2]]$`regioneR::numOverlaps`$shifted.z.scores
# zscores <- (zscores - min(zscores)) + .01
# zscore_freq <- round(zscores, 3) * 1000  # 1E5 precision
# shifts <- rlfs_data[[2]]$`regioneR::numOverlaps`$shifts
# distres <- unlist(lapply(seq(shifts), function(i) {rep(shifts[i], zscore_freq[i])}))
# krt <- moments::kurtosis(distres) / 3
# krt <- ifelse(krt > 1, 1, krt)  # Discount platykurtic
# zscore_summit <- ifelse(zscore_summit > 10, 10, zscore_summit) * 10  # Ensure 100 range, middle is 5
# skw <- moments::skewness(distres)
# rlfs_score <- (pval/minpvalpossible) * zscore_summit * krt / (abs(skw) + 1)



```

Quality score: 





***

## Details

<hr>


```{r child='annotation_template.Rmd', eval=show_anno}
```


```{r child='rlfs_template.Rmd', eval=show_rlfs}
```


```{r child='correlation_template.Rmd', eval=show_corr}
```


### Peak calling

```{r}
controlstr <- ifelse(control, "was", "was <strong style='color: red'>not</strong>")
opt1 <- " the MACS2 peaks which overlapped with EPIC2 peaks were considered the 'final' peakset by RSeq."
opt2 <- " the EPIC2 peaks were considered the 'final' peakset by RSeq."

if (mode %in% c("DRIP", "DRIPc", "sDRIP", 'qDRIP', 'RDIP', 'ssDRIP')) {
  if (control) {
    outbed <- peak_ol$overlappingPeaks$`MACS2///EPIC2`
    outbedgr <- toGRanges(outbed[,c(2:4, 7, 6)])
    opt <- opt1
  } else {
    outbedgr <- peak_ol$all.peaks$EPIC2
    opt <- opt2
  }
} else if (mode %in% c("R-ChIP", "RR-ChIP", "RNH-CnR", "MapR", 'DRIVE')) {
  outbed <- peak_ol$overlappingPeaks$`MACS2///EPIC2`
  outbedgr <- toGRanges(outbed[,c(2:4, 7, 6)])
  opt <- opt1
}
peak_protocol <- paste0("Because the mode was <strong>", mode, "</strong> and there ", controlstr, 
                        " a control sample (e.g., genomic input), ", opt)
total_peaks <- length(outbedgr)
total_peaks_color <- ifelse(total_peaks < 3000, 'red', ifelse(total_peaks < 6000, 'orange', 'green'))
```

The peak callers `macs2` and `epic2` were used to call <strong>`r strandedness`</strong> peaks from the bam files. `r peak_protocol` 

Please see the <a href="https://github.com/millerh1/RSeq"  target="_blank">RSeq documentation</a> for a full explanation of the peak analysis approach. 

Number of peaks in final RSeq peakset: <strong style="color: `r total_peaks_color`">`r total_peaks`</strong>

#### Peak MACS2 and EPIC2 overlap statistics

```{r}
res <- suppressMessages(suppressWarnings(makeVennDiagram(peak_ol, ignore.strand = FALSE, margin = .05,
                                         fill = c('skyblue', 'firebrick'))))
```


```{r}
venn_counts <- res$vennCounts
peak_stats <- data.frame(
  "MACS2" = venn_counts[c(3:4),c(4)],
  "EPIC2" = venn_counts[c(2, 4),c(5)],
  row.names = c("Distinct Peak Count", "Overlapping Peak Count")
)
peak_stats['Percentage Peaks Overlapping',] <- c(round(100*(peak_stats$MACS2[2]/sum(peak_stats$MACS2)), 1),
                                           round(100*(peak_stats$EPIC2[2]/sum(peak_stats$EPIC2)), 1))
kable(peak_stats) %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "striped")
```


***

### Read quality

From `fastp` report:

```{r}
before_filter <- unlist(read_qc_data$summary$before_filtering)
after_filter <- unlist(read_qc_data$summary$after_filtering)
namestable <- gsub(names(after_filter), pattern = "_", replacement = " ")
namestable <- stringr::str_to_title(namestable)
namestable <- gsub(namestable, pattern = "Gc", replacement = "GC")
namestable[1:4] <- paste0(namestable[1:4], " (millions)")
read_qc <- tibble(
  "attribute" = namestable,
  "Before filtering" = before_filter,
  "After filtering" = after_filter
) %>% 
  mutate_at(.vars = c("Before filtering", "After filtering"), function(x) {
    ifelse(x > 1000000, x / 1000000, x)
  }) %>% tibble::column_to_rownames(var = "attribute") 
reads_before <- read_qc$`Before filtering`[1]
reads_after <- read_qc$`After filtering`[1]
percent_passing <- round(100*(reads_after/reads_before), digits = 1)
read_qc_color <- ifelse(percent_passing > 90, "green", ifelse(percent_passing > 80, "orange", "red"))
kable(read_qc) %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "striped")
```

Percent reads passing filter: <strong style="color: `r read_qc_color`">`r percent_passing`</strong>

***

### Mapping quality

```{r}
total_reads <- bam_stats$total_reads / 1e6
reads_aligned <- bam_stats$reads_aligned / 1e6
duplicate_reads <- bam_stats$duplicate_reads / 1e6
pct_aligned <- round(100*(reads_aligned/total_reads), digits = 2)
pct_align_color <- ifelse(pct_aligned > 80, "green", ifelse(pct_aligned > 60, "orange", "red"))
pct_duplicated <- round(100*(duplicate_reads/total_reads), digits = 2)
pct_duplicated_color <- ifelse(pct_duplicated < 35, "green", ifelse(pct_aligned < 50, "orange", "red"))
genome <- configlist$genome
```

Reads were aligned to **`r genome`** with `bwa mem`. 

Total reads (millions): **`r total_reads`**

Aligned reads (millions): **`r reads_aligned`**

Percent of reads aligned: <strong style="color: `r pct_align_color`">`r pct_aligned`</strong>

Duplicated reads (millions): **`r duplicate_reads`**

Percent of reads duplicated: <strong style="color: `r pct_duplicated_color`">`r pct_duplicated`</strong>



&nbsp;
<hr />
<p style="text-align: center;">RSeq © 2020, <a href="https://gccri.bishop-lab.uthscsa.edu/"  target="_blank">Bishop Lab</a>, UT Health San Antonio</p>
<p style="text-align: center;">RSeq maintainer: <span style="color: #808080;"><em>millerh1@uthscsa.edu</em></span></p>

&nbsp;






