---
title: "RSeq Report"
output: 
  html_document:
    code_folding: hide
    theme: flatly
    highlight: textmate
params:
  corr_data: "placeholder"
  anno_data: "placeholder"
  rlfs_data: "placeholder"
  bam_stats: "placeholder"
  peak_ol: "placeholder"
  read_qc_data: "placeholder"
  configlist: "placeholder"
  helper_dir: "placeholder"
  total_peaks: "placeholder"
---

```{r setup, include=FALSE, echo=FALSE}
# Need to refactor to call libraries from namespace ::
library(knitr)
library(kableExtra)
library(pheatmap)
library(xgboost)
library(ggpubr)
library(RColorBrewer)
library(ChIPpeakAnno)
library(regioneR)
library(grid)
library(plotly)
show_anno <- ifelse(tibble::is_tibble(anno_data), TRUE, FALSE)
show_corr <- ifelse(is.list(corr_data), TRUE, FALSE)
show_rlfs <- ifelse(is.list(rlfs_data), TRUE, FALSE)
correct_mode <- configlist$mode %in% c("DRIP", "DRIPc", "sDRIP", 'qDRIP')
show_summary <- show_anno & show_corr & correct_mode
if (show_anno) {
  needed_categories <- c("Exon", "LINE", 'SINE', 'TTS', 'Intron')
  if (any(! needed_categories %in% anno_data$Annotation)) {
    show_summary <- FALSE
  }
}
sample_name <- configlist$sample_name
control <- ifelse(configlist$control == "None", FALSE, TRUE)
mode_now <- configlist$mode
current_time <- date()
pe <- configlist$paired_end
genome <- configlist$genome
strand <- configlist$strand_specific
strandedness <- ifelse(strand, "stranded", "unstranded")
moiety <- configlist$moeity
ip_type <- configlist$ip_type
rmap_samples <- file.path(helper_dir, 'data', 'RMapDB_samples_11_13_2020.csv')
rmap_samples <- read_csv(rmap_samples)
rmap_samples$mode_group <- ifelse(rmap_samples$mode %in% c("RNH-CnR", "MapR"), "MapR",
                                  ifelse(rmap_samples$mode %in% c("DRIP", "DRIPc", "sDRIP", 'qDRIP'), 'DRIP',
                                         ifelse(rmap_samples$mode %in% c("RDIP"), "RDIP",
                                                ifelse(rmap_samples$mode %in% c("ssDRIP"), "ssDRIP",
                                                      ifelse(rmap_samples$mode %in% c("R-ChIP"), 'R-ChIP', "../../misc")))))
xgb_file <- file.path(helper_dir, 'data', "xgb_DRIP_group_HS_binary_11_17_2020.model")
lm_file <- file.path(helper_dir, 'data', "lm_DRIP_group_HS_nonbinary_11_17_2020.rda")
rmap_quality <- file.path(helper_dir, 'data', 'rmap_quality_DRIP_11_17_2020.csv')
```

<br>

Sample name: <strong>`r sample_name`</strong>

Sample type: <strong>`r paste0(mode_now, "-Seq")`</strong>

Genome: <strong>`r genome`</strong>

Time finished: <strong>`r current_time`</strong>


***

```{r child='summary_score_template.Rmd', eval=show_summary}
```


## Quality Report Details

<hr>


```{r child='annotation_template.Rmd', eval=show_anno}
```


```{r child='rlfs_template.Rmd', eval=show_rlfs}
```


```{r child='correlation_template.Rmd', eval=show_corr}
```


### Peak calling

```{r}
controlstr <- ifelse(control, "was", "was <strong style='color: red'>not</strong>")
opt1 <- " the MACS2 peaks which overlapped with EPIC2 peaks were considered the 'final' peakset by RSeq."
opt2 <- " the EPIC2 peaks were considered the 'final' peakset by RSeq."

if (mode_now %in% c("DRIP", "DRIPc", "sDRIP", 'qDRIP', 'RDIP', 'ssDRIP', 'S1-DRIP')) {
  if (control) {
    opt <- opt1
  } else {
    opt <- opt2
  }
} else if (mode_now %in% c("R-ChIP", "RR-ChIP", "RNH-CnR", "MapR", 'DRIVE')) {
  opt <- opt1
}
peak_protocol <- paste0("Because the mode was <strong>", mode_now, "</strong> and there ", controlstr,
                        " a control sample (e.g., genomic input), ", opt)

# TODO: What should this number be? Can we arrive at a more robust estimate?
total_peaks_color <- ifelse(total_peaks < 3000, 'red', ifelse(total_peaks < 6000, 'orange', 'green'))
```

The peak callers `macs2` and `epic2` were used to call <strong>`r strandedness`</strong> peaks from the bam files. `r peak_protocol`

Please see the <a href="https://github.com/millerh1/RSeq"  target="_blank">RSeq documentation</a> for a full explanation of the peak analysis approach.

Number of peaks in final RSeq peakset: <strong style="color: `r total_peaks_color`">`r total_peaks`</strong>

#### Peak MACS2 and EPIC2 overlap statistics

```{r}
res <- suppressMessages(suppressWarnings(makeVennDiagram(peak_ol, ignore.strand = FALSE, margin = .05,
                                         fill = c('skyblue', 'firebrick'))))
```


```{r}
venn_counts <- res$vennCounts
peak_stats <- data.frame(
  "MACS2" = venn_counts[c(3:4),c(4)],
  "EPIC2" = venn_counts[c(2, 4),c(5)],
  row.names = c("Distinct Peak Count", "Overlapping Peak Count")
)
peak_stats['Percentage Peaks Overlapping',] <- c(round(100*(peak_stats$MACS2[2]/sum(peak_stats$MACS2)), 1),
                                           round(100*(peak_stats$EPIC2[2]/sum(peak_stats$EPIC2)), 1))
kable(peak_stats) %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "striped")
```


***

### Read quality

From `fastp` report:

```{r}
before_filter <- unlist(read_qc_data$summary$before_filtering)
after_filter <- unlist(read_qc_data$summary$after_filtering)
namestable <- gsub(names(after_filter), pattern = "_", replacement = " ")
namestable <- stringr::str_to_title(namestable)
namestable <- gsub(namestable, pattern = "Gc", replacement = "GC")
namestable[1:4] <- paste0(namestable[1:4], " (millions)")
read_qc <- tibble(
  "attribute" = namestable,
  "Before filtering" = before_filter,
  "After filtering" = after_filter
) %>%
  mutate_at(.vars = c("Before filtering", "After filtering"), function(x) {
    ifelse(x > 1000000, x / 1000000, x)
  }) %>% tibble::column_to_rownames(var = "attribute")
reads_before <- read_qc$`Before filtering`[1]
reads_after <- read_qc$`After filtering`[1]
percent_passing <- round(100*(reads_after/reads_before), digits = 1)
read_qc_color <- ifelse(percent_passing > 90, "green", ifelse(percent_passing > 80, "orange", "red"))
kable(read_qc) %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "striped")
```

Percent reads passing filter: <strong style="color: `r read_qc_color`">`r percent_passing`</strong>

***

### Mapping quality

```{r}
total_reads <- bam_stats$total_reads / 1e6
reads_aligned <- bam_stats$reads_aligned / 1e6
duplicate_reads <- bam_stats$duplicate_reads / 1e6
pct_aligned <- round(100*(reads_aligned/total_reads), digits = 2)
pct_align_color <- ifelse(pct_aligned > 80, "green", ifelse(pct_aligned > 60, "orange", "red"))
pct_duplicated <- round(100*(duplicate_reads/total_reads), digits = 2)
pct_duplicated_color <- ifelse(pct_duplicated < 35, "green", ifelse(pct_aligned < 50, "orange", "red"))
genome <- configlist$genome
```

Reads were aligned to **`r genome`** with `bwa mem`. 

Total reads (millions): **`r total_reads`**

Aligned reads (millions): **`r reads_aligned`**

Percent of reads aligned: <strong style="color: `r pct_align_color`">`r pct_aligned`</strong>

Duplicated reads (millions): **`r duplicate_reads`**

Percent of reads duplicated: <strong style="color: `r pct_duplicated_color`">`r pct_duplicated`</strong>



&nbsp;
<hr />
<p style="text-align: center;">RSeq © 2020, <a href="https://gccri.bishop-lab.uthscsa.edu/"  target="_blank">Bishop Lab</a>, UT Health San Antonio</p>
<p style="text-align: center;">RSeq maintainer: <span style="color: #808080;"><em>millerh1@uthscsa.edu</em></span></p>

&nbsp;
